---
title: "ST_503 HW2"
author: "Halid Kopanski"
date: "`r Sys.Date()`"
geometry: "left = 1.75 cm, right = 1.75 cm, top = 1.25 cm, bottom = 2 cm"
output: pdf_document
---

```{r setup, include=FALSE}
library(faraway)
library(tidyverse)
library(ellipse)
```

### LMR 3.4 a)

```{r echo = FALSE}
null_model1 <- lm(total ~ 1, data = sat)
#summary(null_model1)
#knitr::kable(anova(null_model1))

sat_model1 <- lm(total ~ expend + ratio + salary, data = sat)
summary(sat_model1)
knitr::kable(anova(null_model1, sat_model1))
knitr::kable(anova(sat_model1))

SST <- sum((sat$total - mean(sat$total))^2)
SSR <- sum((sat_model1$fitted.values - mean(sat$total))^2)
SSE <- sum((sat$total - sat_model1$fitted.values)^2)
MSR <- SSR/(sat_model1$rank - 1)
MSE <- SSE/(nrow(sat) - sat_model1$rank)
df_vector <- c(sat_model1$rank - 1, nrow(sat) - sat_model1$rank, nrow(sat) - 1)
SS <- c(SSR, SSE, SST)

anova_table <- as_tibble(cbind(df_vector, SS))

anova_table <- anova_table %>% mutate(MS = SS/df_vector)

anova_table[3,3] <- NA

F_stat <- c(as.numeric(anova_table[1,3] / anova_table[2,3]), NA, NA)

p_value <- c(1 - (pf(F_stat[1], (sat_model1$rank - 1) , (nrow(sat) - sat_model1$rank))), NA, NA)

anova_table <- cbind(anova_table, F_stat, p_value)

knitr::kable(anova_table)

```

There is not enough evidence to reject the null hypothesis that $\beta_{salary}$ is zero. The p value is above the critical value of 0.025 for a two sided t test.

There is sufficient evidence to reject the null hypothesis that states $\beta_{expend}$ = $\beta_{ratio}$ = $\beta_{salary}$. The f statistic and the corresponding p value are `r F_stat[1]` and `r p_value[1]` respectively. 

Given the large p values and low $R^2$, we cannot say that the predictors had a large effect on the response variable.

\newpage

### LMR 3.4 b)

```{r echo = FALSE}

sat_model2 <- lm(total ~ expend + ratio + salary + takers, data = sat)
summary(sat_model2)
knitr::kable(anova(null_model1, sat_model2))
knitr::kable(anova(sat_model1, sat_model2))
knitr::kable(anova(sat_model2))

SST <- sum((sat$total - mean(sat$total))^2)
SSR <- sum((sat_model2$fitted.values - mean(sat$total))^2)
SSE <- sum((sat$total - sat_model2$fitted.values)^2)
MSR <- SSR/(sat_model2$rank - 1)
MSE <- SSE/(nrow(sat) - sat_model2$rank)
df_vector <- c(sat_model2$rank - 1, nrow(sat) - sat_model2$rank, nrow(sat) - 1)
SS <- c(SSR, SSE, SST)

anova_table <- as_tibble(cbind(df_vector, SS))

anova_table <- anova_table %>% mutate(MS = SS/df_vector)

anova_table[3,3] <- NA

F_stat <- c(as.numeric(anova_table[1,3] / anova_table[2,3]), NA, NA)

p_value <- c(1 - (pf(F_stat[1], (sat_model2$rank - 1) , (nrow(sat) - sat_model2$rank))), NA, NA)

anova_table <- cbind(anova_table, F_stat, p_value)

knitr::kable(anova_table)

```

We have sufficient evidence to reject the null hypothesis that $\beta_{takers}$ = 0 at the $\alpha$ level of 0.05 (p value in this case is close to zero). 

\newpage

### LMR 3.7 a)

```{r echo = FALSE}
pun_model1 <- lm(Distance ~ RStr + LStr + RFlex + LFlex, data = punting)
summary(pun_model1)
```

None of the predictors are significant at the 5% level

\newpage

### LMR 3.7 b)

```{r echo = FALSE}
null_model1 <- lm(Distance ~ 1, data = punting)
summary(null_model1)
anova(null_model1, pun_model1)

SST <- sum((punting$Distance - mean(punting$Distance))^2)
SSR <- sum((pun_model1$fitted.values - mean(punting$Distance))^2)
SSE <- sum((punting$Distance - pun_model1$fitted.values)^2)
MSR <- SSR/(pun_model1$rank - 1)
MSE <- SSE/(nrow(punting) - pun_model1$rank)
df_vector <- c(pun_model1$rank - 1, nrow(punting) - pun_model1$rank, nrow(punting) - 1)
SS <- c(SSR, SSE, SST)

anova_table <- as_tibble(cbind(df_vector, SS))

anova_table <- anova_table %>% mutate(MS = SS/df_vector)

anova_table[3,3] <- NA

F_stat <- c(as.numeric(anova_table[1,3] / anova_table[2,3]), NA, NA)

p_value <- c(1 - (pf(F_stat[1], (pun_model1$rank - 1) , (nrow(punting) - pun_model1$rank))), NA, NA)

anova_table <- cbind(anova_table, F_stat, p_value)

knitr::kable(anova_table)
```

\newpage

### LMR 3.7 c)
```{r echo = FALSE}
pun_model2 <- lm(Distance ~ RStr + LStr, data = punting)
summary(pun_model2)

```

\newpage

### LMR 3.7 d)

```{r echo = FALSE}
confint(pun_model1)

plot(ellipse(pun_model1, c(2,3)), type = 'l')
points(pun_model1$coefficients[2], pun_model1$coefficients[3], pch = 19)
abline(v = confint(pun_model1)[2, ], lty = 2)
abline(h = confint(pun_model1)[3, ], lty = 2)
```